---
title: "IIUM Wifi Quality Survery"
author: "Khairul Fathi"
output:
  html_notebook:
    fig_caption: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

# Introduction

Some text for introduction to this survey and results.


# Results

## Data Preparation

Student survey has been conducted for 2 weeks and received 51 total reponses.

Load all required libraries that will be used throughout this analysis.
```{r Library, message=FALSE, warning=FALSE, paged.print=FALSE}
library(plyr)
library(psych)
library(plotly)
```

Start reading both CSV files, from student survey and speedtest result.
```{r ReadCSV, message=FALSE, warning=FALSE, paged.print=FALSE}
csv_surv <- read.csv('Student_Survey.csv')
csv_test <- read.csv('Speedtest_Result.csv')
```


Rename variables name to something more meaningful, shorter and easier to code.
```{r DataPrep, message=FALSE, warning=FALSE, paged.print=FALSE}
tmpstud <- plyr::rename(csv_surv, c(Academic.Programme = "Programme", Internet.Connection.Method = "SSID", Main.Usage.of.Internet = "Usage", On.overall.basis..how.satisfied.are.you.with.wireless.internet.connection.provided.by.IIUM. = "Satisfaction", Propose.a.solution.to.improve.IIUM.WIFI.services. = "Comment", Average.Duration.of.Daily.Use.of.Internet = "Duration", How.many.times.have.your.Internet.connection.been.suddenly.disconnected.or.face.intermittent.connection.in.past.3.days. = "Disconnected", Is.WiFi.coverage.adequate.and.within.acceptable.signal.strength. = "Coverage", How.satisfied.are.you.with.the.network.speed.to.achieve.your.main.usages. = "Speed"))

tmptest <- plyr::rename(csv_test, c(Submission.Date = "Timestamp", WiFi.SSID = "SSID", Download.Speed..Mbps. = "DLSpeed", Download.Size..MB. = "DLSize", Upload.Speed..Mbps. = "UPSpeed", Upload.Size..MB. = "UPSize", Ping..ms. = "Ping", Jitter..ms. = "Jitter", Loss.... = "Loss", Signal.Strength..dBm. = "Signal"))

```

Perform data cleansing
```{r DataCleanse, message=FALSE, warning=FALSE, paged.print=FALSE}
tmpstud <- tmpstud[which(tmpstud$Gender == ''), ]
tmpstud$Timestamp <- tmpstud$Gender <- tmpstud$Comment <- NULL
tmpstud$Usage[7] <- "Study and assignment, Topic and subject research, Casual browsing"
tmpstud$Usage <- strsplit(as.character(tmpstud$Usage), ",")
```


Split Usage into list and transpose into dataframe
```{r Transpose, message=FALSE, warning=FALSE, paged.print=FALSE}
k <- 1

Respondent <- integer()
Programme <- character()
SSID <- character()
Mahallah <- character()
Usage <- character()
Satisfaction <- integer()
Duration <- character()
Speed <- integer()
Disconnected <- character()
Coverage <- character()

for(i in 1:nrow(tmpstud))
{
  for(j in 1:3)
  {
    Respondent[k] <- i # to identify unique number of respondent
    Programme[k] <- as.character(tmpstud$Programme[i])
    SSID[k] <- as.character(tmpstud$SSID[i])
    Mahallah[k] <- as.character(tmpstud$Mahallah[i])
    Usage[k] <- trimws(tmpstud$Usage[[i]][j]) # trim leading and trailing whitespace
    Satisfaction[k] <- tmpstud$Satisfaction[i]
    Duration[k] <- as.character(tmpstud$Duration[i])
    Speed[k] <- tmpstud$Speed[i]
    Disconnected[k] <- as.character(tmpstud$Disconnected[i])
    Coverage[k] <- as.character(tmpstud$Coverage[i])
    
    k <- k + 1
  }
}
```


Finalized dataframe from previous step
```{r MainDF, message=FALSE, warning=FALSE, paged.print=FALSE}
dfstud <- data.frame(Respondent, Programme, SSID, Mahallah, Usage, Satisfaction, Duration, Speed, Disconnected, Coverage, stringsAsFactors = FALSE)
```

## Overall Level of Satisfaction

Bar graph for overall satisfaction
```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=TRUE}
dfsatisfaction <- count(unique(dfstud[, c(1,6)])[, 2])
dfsatisfaction$x[dfsatisfaction$x == 1] <- "Very Dissatisfied"
dfsatisfaction$x[dfsatisfaction$x == 2] <- "Dissatisfied"
dfsatisfaction$x[dfsatisfaction$x == 3] <- "Satisfied"
dfsatisfaction$x[dfsatisfaction$x == 4] <- "Very Satisfied"

plot_ly(x = dfsatisfaction$x, y = dfsatisfaction$freq, type = "bar") %>%
layout(title = 'Overall Level of Satisfaction', yaxis = list(title = "Respondent"), xaxis = list(title = "Satisfaction Level"))
```